MAESTROeX: A Massively Parallel Low Mach Number Astrophysical Solver

### 2019-03-13 MAESTROeX_I/paper.tex
description of React State

There are a few key numerical modules we use in each time step.
\begin{itemize}
\item {\bf Enforce HSE} computes the base state pressure, $p_0$, from a base state density, $\rho_0$ by integrating the hydrostatic equilibrium condition in 1D (see equation (A10) in \cite{MAESTRO_V}).  The base state pressure remains equal to a constant value from the location of a prescribed cutoff density outward for the entire simulation.
\item {\bf React State}
\end{itemize}

@@

Call {\bf React State}$[(\rho X_k)^n, (\rho h)^n, p_0^n] \rightarrow [(\rho X_k)^{(1)}, (\rho h)^{(1)}, (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)}]$.
\MarginPar{AJN: I think we can simplify the description here... this is somewhat confusing now.}

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ using a Godunov approach \citep{XRB_III}.
\MarginPar{We may not need $\rho_0$ if we predict $\rho X$ or $\rho$ and $X$.  AJN: If we end up keeping prediction of $\rho'$ and $X$, and $(\rho h)'$ we need to summarize this, particularly since $\rho_0$ and $(\rho h)_0$ treatment differs from previous papers.}

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ usingusing a Godunov approach \citep{XRB_III}.

@@

\item Update the enthalpy.  This step is identical to {\bf Step 4D} except we use
  the updated values $\uadvtwo, \rho_0^{n+1}, (\rho h)_0^{n+1}$, and $p_0^{n+\myhalf}$
  rather than
  $\uadvone, \rho_0^{n+1,\star}, (\rho h)_0^{n+1,\star}$, and $p_0^n$.
  In particular:
\MarginPar{Again, we may not need $\rho_0$ and $(\rho h)_0$.}

>>>>

There are a few key numerical modules we use in each time step.
\begin{itemize}
\item {\bf Enforce HSE} computes the base state pressure, $p_0$, from a base state density, $\rho_0$ by integrating the hydrostatic equilibrium condition in 1D (see equation (A10) in \cite{MAESTRO_V}).  The base state pressure remains equal to a constant value from the location of a prescribed cutoff density outward for the entire simulation.
\item {\bf React State} advances the species and enthalpy due to reactions over $\Delta t/2$ by integrating
\begin{equation}
\frac{dX_k}{dt} = \dot\omega_k(\rho,X_k,T); \qquad
\frac{dT}{dt} = \frac{1}{c_p}\left(-\sum_k\xi_k\dot\omega_k + H_{\rm nuc}\right)
\end{equation}
The inputs are the species, enthalpy, and base state pressure, and the outpus are the species, enthalpy, reaction rates, and nuclear energy generation rate.
See \cite{MAESTRO_III,MAESTRO_V} for details.
\end{itemize}

@@

Call {\bf React State}$[(\rho X_k)^n, (\rho h)^n, p_0^n] \rightarrow [(\rho X_k)^{(1)}, (\rho h)^{(1)}, (\rho \omegadot_k)^{(1)}, (\rho \Hnuc)^{(1)}]$.

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ using a Godunov approach \citep{XRB_III}.
\MarginPar{mention $\rho'$ and $X$ advection; $(\rho h)'$ advection}

@@

\item Compute the time-centered species edge states, $(\rho X_k)^{\nph,\pred}$,
  for the conservative update of $(\rho X_k)^{(1)}$ using a Godunov approach \citep{XRB_III}.

@@

\item Update the enthalpy.  This step is identical to {\bf Step 4D} except we use
  the updated values $\uadvtwo, \rho_0^{n+1}, (\rho h)_0^{n+1}$, and $p_0^{n+\myhalf}$
  rather than
  $\uadvone, \rho_0^{n+1,\star}, (\rho h)_0^{n+1,\star}$, and $p_0^n$.
  In particular:
